Making Sequential Programs Deterministic

### 2019-03-30 experiments.tex
experiments: NONDEX on Randoop

\subsection{Running NONDEX on Randoop}
To evaluate how existing tools perform on large programs, we ran NONDEX~\cite{nondex-tool} on Randoop~\cite{randoop-tool}.
\begin{itemize} 
    \item Ran randoop with NonDex, instructions from cite.
    \item didn't find any flakiness issues in the FULL mode.
    \item \todo{check if the bugs discovered by \theDeterminismChecker have test coverage}
\end{itemize}

>>>>

\subsection{Running NONDEX on Randoop}
To evaluate how existing tools perform on large programs, we ran the tool \href{https://github.com/TestingResearchIllinois/NonDex}{NONDEX~\cite{nondex}} on 
\href{https://github.com/randoop/randoop}{Randoop~\cite{randoop}}.
We followed the instructions to build the project with the gradle plugin. 
NONDEX terminated in approximately 20 seconds and didn't report any flaky tests.
\todo{check if the bugs discovered by \theDeterminismChecker have test coverage}
\todo{We investigated the tests covering code that \theDeterminismChecker reported as nondeterministic.
If code is covered by tests, NONDEX couldn't discover it. Else, its a limitation of NONDEX}.
This indicates that the additional programmer effort required by \theDeterminismChecker is justified
as our tool discovers non-trivial issues and doesn't depend on code coverage or runtime heuristics.
